Methods and Results

### 2022-09-20 ms.Rmd
Adding section on variation
MLMA Variance analysis added for CVR and VR

>>>>

#### Variation in female fitness

```{r, variation}

  ###############
      # Variance in female fitness in harm and control treatment. Use lnCVR and lnVR (Nakagawa et al. 2015). On request of reviewer
  ################

    ## Overall intercept only models. Note that, for lnCVR, 3 effect sizes are based on non-ratio data so are not defined and are excluded.
    model1_lnCVR <- rma.mv(logCVR ~ 1, V = v_logCVR, 
                       random = list(~1|study, ~1|obs, ~1|species), dfs = "contain", test = "t", 
                       method = "REML", data = data)
    robust_model1_lnCVR <- robust(model1_lnCVR, cluster = data$study, vcov = "CR2")

    model1_lnVR <- rma.mv(logVR ~ 1, V = v_logVR, 
                       random = list(~1|study, ~1|obs, ~1|species), dfs = "contain", test = "t", 
                       method = "REML", data = data)
    robust_model1_lnVR <- robust(model1_lnVR, cluster = data$study, vcov = "CR2")

    orchard_plot(model1_lnCVR, group = "study", data = data, 
                 xlab = "log Coefficient of Variation (lnCVR)") + 
    labs(x = "Overall Mean Estimate")
  ###############
      # Final tables
  ################
  # Tables
                n1.7 <- sperm_data %>% group_by(SCR.SCI) %>% summarise(n = n(), nstdy = length(unique(study)), moderator = unique(SCR.SCI))
      n1.7[3,c(2,3)] <- t(c(dim(data)[1], with(data, length(unique(study)))))
  robust_model1.7_PI <- pred_interval(robust_model1.7_reparam, c(4.404, 1.88, 2.49)) # Ignore PIs not used and not correct
  robust_model1.7_PI <- cbind(robust_model1.7_PI, n1.7)
